---
title: "Assignment b04"
author: "Xiao Hu"
date: "`r Sys.Date()`"
output: github_document
---
```{r}
library(tidyverse)
library(tidytext)
library(janeaustenr)
library(palmerpenguins)
library(purrr)
library(testthat)
```


# Exercise 1 (37.5 points)
Take a Jane Austen book contained in the `janeaustenr` package, or another book from some other source, such as one of the many freely available books from Project Gutenberg (be sure to indicate where you got the book from). Make a plot of the most common words in the book, removing “stop words” of your choosing (words like “the”, “a”, etc.) or stopwords from a pre-defined source, like the stopwords package or `tidytext::stop_words`.

```{r}
# tibble aka neater data frame
emma_df <- data_frame(Text = emma) 
# picks out the individual words and places them as rows
emma_words <- emma_df %>% 
                  unnest_tokens(output = word, input = Text) 
# remove stopwords
emma_words <- emma_words %>%
                   anti_join(stop_words, by = "word") 
# counts of the words
emma_wordcounts <- emma_words %>% count(word, sort = TRUE)

# top 10 words with highest frequency
top_10 <- emma_wordcounts %>% 
  arrange(desc(n)) %>% 
  head(10) 

# plot
top_10 %>% 
    ggplot(aes(reorder(word,n), n)) + 
    geom_col() +
    coord_flip() +
    labs(x = "Word \n", y = "\n Count ", title = "Frequent Words In Emma \n") +
    geom_text(aes(label = n), hjust = 1.2, colour = "white", fontface = "bold") +
    theme(plot.title = element_text(hjust = 0.5), 
        axis.title.x = element_text(face="bold", size = 10),
        axis.title.y = element_text(face="bold", size = 10))
```


# Exercise 2 (37.5 points)
Make a function that converts words to your own version of Pig Latin.

```{r}
#' Converts one word to the version of Pig Latin
#'
#' For words that begin with consonant sounds, all letters before the initial vowel are reversed.
#' If the last letter is a consonant sound, then add "y" to the end of the word, 
#' otherwise, add "e" to the end of the word.
#'
#' @param word a string
#' @return A string
#' @examples
#' pig_latin("ieuoaords")
#' pig_latin("posdhla")
#' 
#' @export


pig_latin <- function(word){
  
  stopifnot(is.character(word))
  #For words that begin with consonant sounds, all letters before the initial vowel are reversed
  list = c("a","e","i","o","u")
  i = 1
  while (i <= nchar(word) & (substr(word,i,i) %in% list) ){
    i = i+1
    
  }
  if (i > 1){
    cons = substr(word,1,i-1)
    splits <- strsplit(cons, "")[[1]]
    reversed <- rev(splits)
    reversed_cons <- paste(reversed, collapse = "")
    pig_latin <- str_c(reversed_cons, str_sub(word,i))
  }else{
    pig_latin <- word
  }
  
  #If the last letter is consonant sounds, then add "y" to the end of the word, 
  #otherwise, add "e" to the end of the word.
  if (str_sub(pig_latin,-1) %in% list){
    pig_latin <- str_c(pig_latin,"y")
  }else{
    pig_latin <- str_c(pig_latin,"e")
  }
  
  return(pig_latin)  
}
```

```{r}
test_that("Testing pig_latin function", {
  expect_equal(pig_latin("lihjgka"),"lihjgkay")
  expect_equal(pig_latin("aeojgka"),"oeajgkay")
  expect_match(pig_latin("ljgk"), 'ljgke')
  expect_error(pig_latin(1), "is.character")
})
```

# Exercise 3 (37.5 points)
For this exercise, you’ll be evaluating a model that’s fit separately for each group in some dataset. You should fit these models with some question in mind.

In this exercise, I will use `penguins` as my dataset to investigate the relationship between bill depth and body mass across different species.

```{r}
penguins <- na.omit(penguins)
head(penguins)
```

1. Make a column of model objects. Do this using the appropriate mapping function from the purrr package. Note: it’s possible you’ll have to make use of nesting, here.
```{r}
models <- penguins %>% 
            nest(data = -species) %>% 
            mutate(
              model = map(data, 
                          function(df) lm(body_mass_g ~ bill_depth_mm,
                                data = df)
                          )
            )
models
```
I fitted a linear regression with body mass as response variable and bill depth as explanatory variable for each species.

2. Evaluate the model in a way that interests you. But, you should evaluate something other than a single number for each group. Hint: you’ll need to use another purrr mapping function again.
```{r}
models <- models %>% 
            mutate(
                pred = map(.x = model, ~predict(.x)),
                beta_bill_depth = map_dbl(.x = model, ~coef(.x)['bill_depth_mm']),
                significance = map_dbl(.x = model, ~glance(.x) %>% pull(p.value))
                )
```

I extracted coefficient of bill_depth and its p-value in each model to check whether there are any differences between coefficients among different species and whether all the coefficients are significant. Moreover, I also predicted body mass using the fitted linear regression model, and the values are stored in a tibble for each species.

3. Print out this intermediate tibble for inspection (perhaps others as well, if it makes sense to do so).
```{r}
models
```

All coefficients are positive and significant. Gentoo has the largest coefficient, which indicates that one unit change in bill depth is associated with the most changes in body mass (369.44g).

4. Unnest the resulting calculations, and print your final tibble to screen. Make sure your tibble makes sense: column names are appropriate, and you’ve gotten rid of columns that no longer make sense.
```{r}
unnest_t <- models %>% select(-model) %>% unnest(cols = c(data,pred)) %>% select(species,bill_depth_mm,body_mass_g,pred,beta_bill_depth,significance)
unnest_t
```

5. Produce a plot communicating something about the result.
```{r}
unnest_t %>% ggplot(aes(y = body_mass_g,x = bill_depth_mm)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red") +
  facet_wrap(~species)
```

The red lines represent predicted value by linear regression models. It is clear that the linear model fits data well for all species, and there are differences in association between bill depth and body mass across different species. Gentoo has the steepest slope, while slope in Adelie and Chinstrap are similar.

