---
title: "Assignment b04"
author: "Xiao Hu"
date: "`r Sys.Date()`"
output: html_document
---
```{r}
library(tidyverse)
library(tidytext)
library(janeaustenr)
library(palmerpenguins)
library(purrr)
#install.packages("tidytext")
```


# Exercise 1 (37.5 points)
Take a Jane Austen book contained in the `janeaustenr` package, or another book from some other source, such as one of the many freely available books from Project Gutenberg (be sure to indicate where you got the book from). Make a plot of the most common words in the book, removing “stop words” of your choosing (words like “the”, “a”, etc.) or stopwords from a pre-defined source, like the stopwords package or `tidytext::stop_words`.

```{r}
# tibble aka neater data frame
emma_df <- data_frame(Text = emma) 
# picks out the individual words and places them as rows
emma_words <- emma_df %>% 
                  unnest_tokens(output = word, input = Text) 
# remove stopwords
emma_words <- emma_words %>%
                   anti_join(stop_words, by = "word") 
# counts of the words
emma_wordcounts <- emma_words %>% count(word, sort = TRUE)

# top 10 words with highest frequency
top_10 <- emma_wordcounts %>% 
  arrange(desc(n)) %>% 
  head(10) 

# plot
top_10 %>% 
    ggplot(aes(reorder(word,n), n)) + 
    geom_col() +
    coord_flip() +
    labs(x = "Word \n", y = "\n Count ", title = "Frequent Words In Emma \n") +
    geom_text(aes(label = n), hjust = 1.2, colour = "white", fontface = "bold") +
    theme(plot.title = element_text(hjust = 0.5), 
        axis.title.x = element_text(face="bold", size = 10),
        axis.title.y = element_text(face="bold", size = 10))
```


# Exercise 2 (37.5 points)
Make a function that converts words to your own version of Pig Latin.
Your Pig Latin should incorporate two components:

Rearrangement component

The default Pig Latin rearrangement rule, as per Wikipedia, moves beginning letters to the end:

For words that begin with consonant sounds, all letters before the initial vowel are placed at the end of the word sequence.
When words begin with consonant clusters (multiple consonants that form one sound), the whole sound is added to the end
For words beginning with vowel sounds, one removes the initial vowel(s) along with the first consonant or consonant cluster.
Modify this somehow. Maybe you move letters from the end to the beginning, or you change the rules altogether, keeping a similar level of complexity.

Addition component

The default Pig Latin addition rule is to add “ay” to the end of the word, after rearranging the letters of the word. You should choose some other addition rule.
```{r}

pig_latin <- function(word){
  #For words that begin with consonant sounds, all letters before the initial vowel are reversed
  list = c("a","e","i","o","u")
  i = 1
  while (i <= nchar(word) & (substr(word,i,i) %in% list) ){
    i = i+1
    
  }
  if (i > 1){
    cons = substr(word,1,i-1)
    splits <- strsplit(cons, "")[[1]]
    reversed <- rev(splits)
    reversed_cons <- paste(reversed, collapse = "")
    pig_latin <- str_c(reversed_cons, str_sub(word,i))
  }else{
    pig_latin <- word
  }
  
  #If the last letter is consonant sounds, then add "y" to the end of the word, 
  #otherwise, add "e" to the end of the word.
  if (str_sub(pig_latin,-1) %in% list){
    pig_latin <- str_c(pig_latin,"y")
  }else{
    pig_latin <- str_c(pig_latin,"e")
  }
  
  return(pig_latin)  
}
```

```{r}
word <- "ieuoaords"
pig_latin(word)
word <- "posdhla"
pig_latin(word)
```

# Exercise 3 (37.5 points)
For this exercise, you’ll be evaluating a model that’s fit separately for each group in some dataset. You should fit these models with some question in mind.

```{r}
penguins <- na.omit(penguins)
head(penguins)
```

1. Make a column of model objects. Do this using the appropriate mapping function from the purrr package. Note: it’s possible you’ll have to make use of nesting, here.
```{r}
models <- penguins %>% 
            nest(data = -species) %>% 
            mutate(
              model = map(data, 
                          function(df) lm(body_mass_g ~ bill_depth_mm,
                                data = df)
                          )
            )
models
```

2. Evaluate the model in a way that interests you. But, you should evaluate something other than a single number for each group. Hint: you’ll need to use another purrr mapping function again.
```{r}
models <- models %>% 
            mutate(
                pred = map(.x = model, ~predict(.x)),
                beta_bill_depth = map_dbl(.x = model, ~coef(.x)['bill_depth_mm']),
                significance = map_dbl(.x = model, ~glance(.x) %>% pull(p.value))
                )
```

3. Print out this intermediate tibble for inspection (perhaps others as well, if it makes sense to do so).
```{r}
models
```

4. Unnest the resulting calculations, and print your final tibble to screen. Make sure your tibble makes sense: column names are appropriate, and you’ve gotten rid of columns that no longer make sense.
```{r}
unnest_t <- models %>% select(-model) %>% unnest(cols = c(data,pred)) %>% select(species,bill_depth_mm,body_mass_g,pred,beta_bill_depth,significance)
unnest_t
```

5. Produce a plot communicating something about the result.
```{r}
unnest_t %>% ggplot(aes(y = body_mass_g,x = bill_depth_mm)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red") +
  facet_wrap(~species)
```


